Ontology Matching with word2vec

### 2016-04-11 Paper/Draft.tex
Added research questions and hypotheses

 \subsection{Problem}
 We have seen that when information from multiple domains need to be integrated so that it is possible to reason over them together, the ontologies of those domains need to be aligned or merged. Those ontologies contain rules about concepts and concept classes in the shape of triplets, with two concepts and a relation. For example, the rule{\tt Professors are humans} contains the concepts \emph{Professor} and \emph{human} and relationship \emph{being}.

@@

 In summary, ontology aligning is required for multi-domain communication but poses a number of problems that make it difficult for concepts, the building blocks of ontologies, to be matched.
 \subsection{Research questions}

 \subsection{Hypotheses}

>>>>

 \subsection{Problem}
 We have seen that when information from multiple domains needs to be integrated so that it is possible to reason over them together, the ontologies of those domains need to be aligned or merged. Those ontologies contain rules about concepts and concept classes in the shape of triplets, with two concepts and a relation. For example, the rule{\tt Professors are humans} contains the concepts \emph{Professor} and \emph{human} and relationship \emph{being}.

@@

 In summary, ontology aligning is required for multi-domain communication but poses a number of problems that make it difficult for concepts, the building blocks of ontologies, to be matched.
 \subsection{Research questions}
 Can distributed representations of concepts be used to find relationships between concepts in ontologies better than existing terminological matchers?

 Can distributed representations use the context of a concept to find relationships between concepts in ontologies better than existing structural matchers?

 Can distributed representations perform well in a domain it was not designed for?

 \subsection{Hypotheses}
 Since multiple implementations of the algorithm are considered, every hypothesis that follows is considered for every implementation.

 \textit{The distributed representations of concepts matcher can find relationships between concepts in ontologies better than existing terminological matchers.}

 \textit{The distributed representations matcher can use the context of a concept to find relationships between concepts in ontologies better than existing structural matchers.}

 \textit{The distributed representations matcher can perform well in a domain it was not designed for.}

 The following hypotheses are true if for at least one implementation the corresponding hypothesis is true.

 \textit{A distributed representations of concepts matcher can find relationships between concepts in ontologies better than existing terminological matchers.}

 \textit{A distributed representations matcher can use the context of a concept to find relationships between concepts in ontologies better than existing structural matchers.}

 \textit{A distributed representations matcher can perform well in a domain it was not designed for.}
